\chapter{Requirements}
The application visualizes the Netherlands on the screen in 3D. All the buildings that are in the data set are being rendered. There are datasets for the whole of the Netherlands. It is possible to fly over an area of the Netherlands and walk through cities. Besides buildings, also roads and ground type (grass, farm land, water and industrial terrain) are rendered.
Because of the immensely huge data set of buildings in the Netherlands, this data set is filtered, preprocessed and saved in an efficient format, so that it can be used by the algorithms to construct the world. OpenStreetMap has data about the streets, ground type and trees. That data set is also used to render the world.

\section{Specification of functionality}
The following functionality is implemented in the system.
\begin{itemize}
  \item Read data from the preprocessed BAG dataset.\\
      As mentioned in the previous section. The BAG data set is quite large and not all information is required. A selection of the data set need to be made and outputted in a format which can be processed easily.
    \item Construct buildings from geographic data. \\
       From the (converted) BAG dataset, the geographic information can be used to determine the position and the contour of a building. The dataset does not contain information on the height of buildings, but the total surface area of a building is available. From this information it is possible to approximate the height of a building. For every building, different level of detail is required. The user will be able to see buildings in more detail when he or she walks through the city than when the user would fly over the world. When the user flies over the world then the quality of buildings will have less quality so the system will still be able to render the world with acceptable frame rates.
  \item Construct roads and display roads.\\
  OpenStreetMap can be used to construct the surface of the Netherlands. Roads, rivers, land types and so on are present in the dataset. The system needs to filter the data set and create shapes which can be rendered. Multiple levels of detail will also be required of the surface data.
  \item Display the constructed world in 3D in real time.\\
      Since rendering a whole area, like Noord Brabant, can be quite large, an efficient rendering algorithm has to be designed or used so that the application can be rendered in real time.
\end{itemize} 

\section{Specification of interaction}
There are 2 different modes to change the view. The first view is that you fly through and over a city or landscape. In the second view, the camera of the system will be set to a height around 1.75m. That way you see the world as any human would see it as he or she would walk through the city. From the start, the user is able to select a city he or she would like to visit. The user is then placed somewhere above or within the city and is able to go anywhere the user wants. Also the speed in which the user is walking or flying can be configure so that the user is able to walk quickly though the city or is able to fly towards another city.

\section{Specification of presentation}
The world will be rendered dependent on the position of the user. If the user is inside a city, then all buildings in the proximity of the user will be rendered with high detail. While flying the user is able to go to a higher altitude. Since buildings and other parts will become very small, a lower level of detail can be applied to the elements which have to be rendered. When the user gets even higher then multiple buildings will be combined into one model. At the top level, only the landscape will be rendered. 